---
title: "Untitled"
author: "Immanuel"
date: '2022-04-25'
output: html_document
---

```{r}
library(tidyverse)
library(broom)
library(ggpubr)
setwd("/cloud/project/content/post/2022-04-25-an-interview-test")
```


```{r}
assignments_df = read.csv('assignments.csv')
grades_df = read.csv('grades.csv')
students_df = read.csv('students.csv')
```



Q1. How many students are there?
```{r}
length(unique(students_df$student_id))
```

Q2. How many unique majors are there? How many students are in each major?
```{r}
students_df %>% 
  group_by(major) %>% 
  summarise(count = n())
```


Q3. How many students are in each major by student level?

```{r}
students_df %>% 
  group_by(major,student_level) %>% 
  summarise(count = n())
```

Q4. [Challenge] Using the information from Q3., which major and student level has the least amount of students? (Hint: Use the ungroup() function.)

```{r}
students_df %>% 
  group_by(major,student_level) %>% 
  summarise(count = n()) %>% 
  ungroup() %>% 
  filter(count == min(count))
```


Q5. Create a visualization that displays the frequency of each major. Make this visualization look very professional (i.e., titles and color).
```{r}
students_df %>% 
  group_by(major) %>% 
  summarise(count = n()) %>% 
  ggplot(aes(x = major, y = count, fill = major)) +
  geom_bar(stat = 'identity') +
  labs(x = 'Major', y = 'frequency', title = 'Frequency of Majors') +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = 'bold')) 

```



Q6. Create a visualization that displays the frequency of each major by student level. Make this visualization look very professional (i.e., titles and color). Change the size of the font so that it is presentable.


```{r}
students_df %>% 
  group_by(student_level, major) %>% 
  summarise(count = n()) %>% 
  ggplot(aes(x = major, y = count, fill = major)) +
  geom_bar(stat = 'identity') +
  facet_grid(.~ student_level) +
  labs(x = 'Major', y = 'frequency', title = 'Frequency of Majors') +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = 'bold'),
        axis.text.x = element_text(size = 7)) 
```



Q7. Join the students data frame with grades data frame. Save this data frame with appropriate an appropriate name.

```{r}
gs_df = students_df %>% 
  left_join(grades_df, by = 'student_id')
```

Q8. Of the English majors, who performed the worst on assignment 1?


```{r}
tmp_df = gs_df %>% 
  filter(major == 'English', assignment_id == 1)  %>% 
  filter(numeric_grade == min(numeric_grade))
```


Q9. Which assignment did the junior engineer students performed the best on average using their average numeric grade? (Hint: Have to use the ungroup() function again)
```{r}
gs_df %>% 
  filter(student_level == '3-Junior',major == 'Engineering') %>% 
  group_by(assignment_id) %>% 
  summarise(m = mean(numeric_grade)) %>% 
  ungroup() %>% 
  filter(m == max(m))
```


Q10. Which student level performed the best as Statistics and Mathematics major using all their assignments average numeric grade?
```{r}
gs_df  %>% 
  filter(major == 'Statistics and Math') %>% 
  group_by(student_level) %>% 
  summarise(m = mean(numeric_grade)) %>% 
  ungroup() %>% 
  filter(m == max(m))
```


Q11. Join the data frame from question 7 to the assignment data frame. Save this data frame with appropriate an appropriate name.
```{r}
complete_df = gs_df %>% 
  left_join(assignments_df,by = 'assignment_id')
```

Q12. Provide a visualization that displays how students perform on Exams by major and student level. There are a lot of way to approach this question, however, I am interested in what you are able to create. Describe any trends you notice.
```{r}
viz_1_df = complete_df %>% 
  filter(assignment_category == 'Exam') %>% 
  group_by(major,student_level) %>% 
  summarize(m = mean(numeric_grade))  %>% 
  ungroup()


viz_1_df %>% 
  ggplot(aes(x = major, y = m,color = student_level)) +
  geom_point() +
  theme_bw()
```


Seniors do well in science and business
Freshman struggle on business, engineering, English and philosophy compared to the rest of the major
There is a lot of variability in English
students in general do better in statistic and math across all levels



Q13. Using the data frame from question 11, consider only freshman 2nd exam scores (Hint: investigate the *assignment_id* variable) and implement One-Way ANOVA in which you would like to determine if the populations means of performance on the assessment (*numeric_grade*) are the same across major. Answer the following questions to be able to fully grasp the material.


a. Create the data frame that will allow you to answer the statistical question.

```{r}
oneway_aov_df =  complete_df %>% 
  filter(student_level == '1-Freshmen',
         assignment_category == 'Exam',
         assignment_id == 20)
View(oneway_aov_df)
```

b. What is the explanatory and response variables?

- Explanatory Variable: major
- Response Variable: numeric_grade

c. Write the null and alternative hypotheses?

- H0: The populations means of performance on the assessment (*numeric_grade*) are the same across major
- H1: At least one of the populations means of performance on the assessment (*numeric_grade*) of one major is different from the other majors

d. Summarize (Hint: find sample size, mean, standard deviation) and Visualize Data (Hint: box plot and make it look professional).
## Summarize
```{r}
oneway_aov_df %>% 
  group_by(major) %>% 
  summarise(size = n(),
            mean = mean(numeric_grade),
            sd = sd(numeric_grade))
```

## Visualize 
```{r}
oneway_aov_df %>% 
  ggplot(aes(x = major, y = numeric_grade)) +
  geom_boxplot() +
  labs(x = 'Major', y = 'Grade', title = 'Grades by Major') +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, face = 'bold', size = 15))
```



e. Perform and interpret the analysis.

## Perform Analysis
```{r}
model1 <- aov(numeric_grade ~ major, oneway_aov_df)
tidy(model1)
```


## Interpretation Analysis
Weak amount of Evidence against the null hypothesis that the populations means of performance on the assessment (*numeric_grade*) are the same across major




Q14. Using the data frame from question 11, consider only freshman exam scores and implement Two-Way ANOVA in which you would like to determine if the populations means of performance on the assessment (*numeric_grade*) are the same across major and exam number (Hint: turn the *assignment_id* variable into a factor by using the as.factor() function). Answer the following questions to be able to fully grasp the material.


a. Create the data frame that will allow you to answer the statistical question.

```{r}
twoway_aov_df =  complete_df %>% 
  filter(student_level == '1-Freshmen',
         assignment_category == 'Exam'
         ) %>% 
  mutate(assignment_id = as.factor(assignment_id))
View(twoway_aov_df)
```

b. What is the explanatory variables and response variable?

- Explanatory Variable: major and exam number
- Response Variable: numeric_grade

c. Write the null and alternative hypotheses for both explanatory variables?

- H0: The populations means of performance on the assessment (*numeric_grade*) are the same across major
- H1: At least one of the populations means of performance on the assessment (*numeric_grade*) of one major is different from the other majors


- H0: The populations means of performance on the assessment (*numeric_grade*) are the same across exam number
- H1: At least one of the populations means of performance on the assessment (*numeric_grade*) of one exam number is different from the other exam number


d. Summarize (Hint: find sample size, mean, standard deviation) and Visualize Data (Hint: box plot and make it look professional).
## Summarize
```{r}
twoway_aov_df %>% 
  group_by(major,assignment_id) %>% 
  summarise(size = n(),
            mean = mean(numeric_grade),
            sd = sd(numeric_grade))
```

## Visualize 
```{r}


ggboxplot(twoway_aov_df, x = "major", y = "numeric_grade", color = "assignment_id",
          palette = c("#00AFBB", "#E7B800")) +
  labs(x = 'Major', y = 'Performance on Exams by Freshmen', title = 'Box Plot for Two-Way ANOVA with means') +
  theme(plot.title = element_text(hjust = 0.5, face = 'bold', size = 15),
        axis.text.x = element_text(size = 10) )
```


```{r}
ggline(twoway_aov_df, x = "major", y = "numeric_grade", color = "assignment_id",
       add = c("mean_se", "dotplot"),
       palette = c("#00AFBB", "#E7B800"))
```



e. Perform and interpret the analysis.

## Perform Analysis
```{r}
model2 <- aov(numeric_grade ~ major + assignment_id, twoway_aov_df)
summary(model2)
```


## Interpretation Analysis

Strong amount of evidence against the null hypothesis that the populations means of performance on the assessment (*numeric_grade*) are the same across major

No evidence against the null hypothesis that the populations means of performance on the assessment (*numeric_grade*) are the same across exam number
